Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-02 thesis/results.tex
Describing the algorithms used for machine learning, added refs. Started answering heuristics question.

@@

>>>>

\section{Algorithms Used}

A brief description of the machine learning algorithms utilized as well as the
motivation for their inclusion is described below.

\subsection{Random Forest}

The random forest algorithm is a classifier that builds multiple decision trees
with random sets of features. An input is processed by each tree, and the
classification chosen is the one which is produced by most of the trees
\parencite{Ho:1995vm}. For this experiment, the random forest algorithm
generated 10 trees and used 6 random features.

The random forest algorithm was chosen for its unparalleled accuracy and strong
performance \parencite{Leo-Breiman:2004fk}.

\subsection{j4.8}

j4.8 is a free Java version of the C4.5 algorithm, a classifier which builds a
decision tree using the concept of information entropy
\parencite{Quinlan:1993:CPM:152181}. This algorithm was chosen because of it's
successful use in earlier traffic classification publications.

\subsection{Random Tree}

\subsection{Adaboost}

AdaBoost or Adaptive Boosting

@@

    While each phase of the experiment was conducted over a similar time
    period, the number of sessions captured differs greatly. This suggests that
    the Tor network may introduce significant overhead to communications
    streams. How this latency manifests itself will determine how useful it is
    as an identifying characteristic.
